\makenoidxglossaries{}
\newglossaryentry{blocks}{
  name=blocks,
  description={Files where data pertaining to a given network is permanently recorded. A block records some or all of the most recent transactions on the network that have not yet entered any prior blocks. Thus a block is like a page of a ledger or record book.}
}
\newglossaryentry{blockchain}{
  name=blockchain,
  description={A digital ledger in which produced blocks are recorded chronologically and publicly with the transactions in each block.}
}
\newglossaryentry{bond}{
  name=bond,
  description={A privilege granted to users to allow their nodes to mint.}
}
\newglossaryentry{cryptocurrency}{
  name=cryptocurrency,
  plural=cryptocurrencies,
  description={A digital asset designed to work as a medium of exchange that uses cryptography to secure its transactions, to control the creation of additional units, and to verify the transfer of assets.}
}
\newglossaryentry{malicious_entity}{
  name=malicious entity,
  plural=malicious entities,
  description={Any person or malware (malicious software) that brings harm to a computer system. Malware can be in the form of worms, viruses, trojans, spyware, adware and rootkits, etc., which steal protected data, delete documents or add software not approved by a user.}
}
\newglossaryentry{network}{
  name=network,
  description={A group or system of interconnected people or things. In the case of cryptocurrency, a networks is a peer-to-peer digital telecommunications system, allowing nodes to communicate information to each other, such as synchronizing the blockchain.}
}
\newglossaryentry{node}{
  name=node,
  description={Is either a redistribution point or a communication endpoint. A network node is any system that is attached to a network, and is capable of creating, receiving, or transmitting information over a communications channel.}
}
\newglossaryentry{Proof-of-Stake}{
  name=Proof-of-Stake,
  description={A system of minting where power is based on how many coins a person holds. Essentially, new coins are created through block rewards, and any other funds paid to the minters are done through transaction fees paid on existing coins. Instead of mining power being based on how powerful your computer is, PoS will be capable of running on relatively low end computers with sufficient storage. PoS is a type of algorithm by which a cryptocurrency blockchain network aims to achieve distributed consensus.}
}
\newglossaryentry{Proof-of-Work}{
  name=Proof-of-Work,
  description={A system of mining that uses hard-to-compute but easy-to-verify functions to limit exploitation of cryptocurrency mining.}
}
\newglossaryentry{volatile}{
  name=volatile,
  description={In the markets, it is the liability to change rapidly and unpredictably, especially for the worse.}
}
\newglossaryentry{fiat}{
  name=fiat,
  description={A formal authorization or proposition; a decree. Specific to the financial world, a ‘fiat’ currency would be any monetary instrument authorized for trade and distribution by a government or ruling body.}
}
\newglossaryentry{consensus-algorithm}{
  name=consensus algorithm,
  description={May refer to one of several proposed protocols for solving the \gls{consensus} problem in the field of computer science.}
}
\newglossaryentry{consensus}{
  name=consensus,
  description={An agreement among a number of computer processes for a single data value. Examples of applications using consensus include whether to commit a transaction to a database, or agreeing on the identity of someone or something.}
}
\newglossaryentry{Denial-of-Service}{
  name=Denial-of-Service,
  description={A cyber-attack where the perpetrator seeks to make a machine or network resource unavailable to its intended users by temporarily or indefinitely disrupting services of a host connected to the Internet. Denial of service is typically accomplished by flooding the targeted machine or resource with superfluous requests (spam) in an attempt to overload systems and prevent some or all legitimate requests from being fulfilled.}
}
\newglossaryentry{mining}{
  name=mining,
  description={The process by which transactions are verified and added to the public ledger, known as the block chain, and also the means through which new coins are released in a \gls{Proof-of-Work} system.}
}
\newglossaryentry{minting}{
  name=minting,
  description={The process by which transactions are verified and added to the public ledger, known as the block chain, and also the means through which new coins are released in a \gls{Proof-of-Stake} system.}
}
\newglossaryentry{decentralized-system}{
  name=decentralized system,
  plural=decentralized systems,
  description={A system in which multiple parties are required to make their own independent decisions. In the case of cryptocurrency, nodes keep an individual ledger that is synchronized through the network using a \gls{consensus-algorithm}, forming the decentralized system.}
}
\newglossaryentry{transaction}{
  name=transaction,
  description={The act of performing an operation on the blockchain.}
}
\newglossaryentry{ecc-memory}{
  name=error-correcting code memory,
  description={A type of computer data storage that can detect and correct the most common kinds of internal data corruption.}
}
